Considering scale in multilayer animal social networks

### 2020-06-17 paper/manuscript.Rmd
results edits

# Results
Individuals in multilayer networks became more connected as the spatial distance
threshold increased. Mean graph strength differed across habitat layers with
similar and higher graph strength in open and forage layers, and lower strength
in forest layers (Figure \@ref(fig:socres)). Individual graph strength increased
sharply between 5 m and 100 m in all three habitat classes followed by a plateau in
the rate of increase after 100 m (<!--TODO: figure XX-->). 
These results suggest the optimal social scale at
which groups should be assigned is between ~20 - 100 m based on
the rate at which network metrics <!--QW: which metrics?--> stabilized. For ungulates, groups are often
assigned based on 50 m threshold (Lingle 2003; Lesmeries et al. 2018; Peignier
et al. 2019), suggesting that given similar quantities of data, ~50 m is likely
an appropriate social scale for generating social networks in caribou and
similar species. <!--QW: I'm not sure about this statement. Should it be more about 
how GPS data allows (e.g. from this study and Peignier et al; Lesmerises et al.) us to confirm 
the use of 50m buffer that has long been used for studies in the field (e.g. Lingle 2003 and 
any Clutton-Brock red deer paper that uses group size data)-->

Increasing land cover resolution resulted in decreased availability of foraging habitat 
<!--QW: I think we need to call this foraging habitat, when possible... forage to me 
refers to the thing an animal is eating-->,
a rare and patchy habitat, and corresponding low connectivity of individuals in
these habitats at higher resolution (Figure \@ref(fig:lcres)). Graph strength
and edge overlap were relatively consistent across land cover resolutions for
forest and open layers (Figure \@ref(fig:lcres) D, E). Edge overlap decreased
sharply between 30 m and 600 m in forage layers, afterwards remaining stable to
1000 m (Figure \@ref(fig:lcres) D). Graph strength was more variable within
foraging habitat layers across land cover resolutions than open and forest habitat layers (Figure
\@ref(fig:lcres) D). The proportion of relocations in forest and open habitats
increased with increasing spatial resolution, while decreasing in foraging habitat
(Supplementary 1 Figure 1).  Overall, these results indicate the importance of
matching land cover resolution to scale of selection as well as ensuring the
land cover product used has a resolution fine enough to detect landscape
features and habitats relevant to study species, such as important patchy and
rare habitats.
<!--QW: what makes it ordinal again? Is it ordinal OR continuous? -->
The ordinal multilayer network generated indicated within-year time windows of
increased caribou sociality. <!--QW: I'm not sure what you are trying to say in this first sentence. Is it that there are distinct within-year time windows where social network metrics increased? -->
Edge overlap was higher in time windows 1, 6-11 and
15-20 than in time windows 2-5 and 12-15  (Figure \@ref(fig:temp) A). <!--QW: I'm not sure about using the window number - it doesn't really mean anyhting. Can you use actual dates?--> Time
windows of higher edge overlap, between approximately October and May, had
correspondingly higher graph strength compared to time windows of lower edge
overlap, between approximately May and October (Figure \@ref(fig:temp) C). Graph
strength peaked across the time series in periods 9 and 10. These results
suggest that ordinal multilayer networks can effectively capture discrete time
windows of aggregation and dissaggregation related to resource availability, and
highlight the importance of carefully selecting the temporal scale of analysis.

@@

<!-- Figure: metrics by social scale -->
(ref:socres) Varying scale in spatial distance threshold. For each spatial distance threshold (100 - 1000 m by steps of 100 m), multilayer networks were constructed of caribou social associations (*Rangifer tarandus*, n = `r DT[, uniqueN(get(idcol))]` females) on Fogo Island, Newfoundland between `r DT[, format(min(datetime), '%F')]` and `r DT[, format(max(datetime), '%F')]` across three habitat classes (forage, forest, and open). Graph strength (mean of individuals in bold) showed a sharp increase between 5 m and 100 m for all habitat classes. After 100 m, graph strength continued to increase at a slower rate. Open and forage layers showed higher variation in graph strength between individuals while the forest layer had less variation and lower mean graph strength.

<!-- Figure: metrics by land cover resolution -->
(ref:lcres) Varying spatial scale of land cover raster. For each land cover resolution (5, 25, 50, 75, 100, 250 and 500 m), multilayer networks were constructed of caribou social associations (*Rangifer tarandus*, n = `r DT[, uniqueN(get(idcol))]` females) on Fogo Island, Newfoundland between `r DT[, format(min(datetime), '%F')]` and `r DT[, format(max(datetime), '%F')]` across three habitat classes (forage, forest, and open). A, B, C) Three land cover rasters: the original resolution (30 m) and two aggregated rasters (500 m and 1000 m). D) Edge overlap of habitat layers across spatial resolutions. Open and forest layers show consistent edge overlap with increasing spatial resolution while forage shows a sharp decline in edge overlap between 30 m and 600 m. Above 600 m, the forage layers are stable. E) Graph strength (mean of individuals in bold) within habitat layers across spatial resolution. Forage layers showed high variation in graph strength with many individuals dropping to 0 after 500 m and others increasing with spatial resolution. Open layers and forest layers were relatively stable across spatial resolutions, with higher mean graph strength in open compared to forest.

<!-- Figure: metrics by number of observations -->
(ref:nobs) Varying scale in number of observations. Multilayer networks were generated using a  sample number of observations (10 - 1000 observations by steps of 10) of caribou social associations (*Rangifer tarandus*, n = `r DT[, uniqueN(get(idcol))]` females) on Fogo Island, Newfoundland between `r DT[, format(min(datetime), '%F')]` and `r DT[, format(max(datetime), '%F')]` across three habitat classes (forage, forest, and open). A) Graph strength was highly variable at low number of observations (less than 100) for all habitat layers and relatively stable after 200 observations. B) Edge overlap increased for all habitat layers with increasing number of observations. Open and forage layers had higher edge overlap than forest layers. C) Multidegree increased for all individuals with increasing number of observations. Individuals showed high variability (`r nobs[nobs == max(nobs), paste(range(multideg), collapse = ' - ')]`) at the maximal number of observations (1000).

<!-- Figure: Time window -->
(ref:temp) Varying temporal scale in multilayer networks. Multilayer networks were generated of caribou social associations (*Rangifer tarandus*, n = `r DT[, uniqueN(get(idcol))]` females) on Fogo Island, Newfoundland within ordinal time windows (20 ordinal sample periods of 35-36 days) between `r DT[, format(min(datetime), '%F')]` and `r DT[, format(max(datetime), '%F')]`. A) Edge overlap across time windows showed two periods of low overlap (time windows 2-5 and 12-15), and three periods of high overlap (time windows 1, 6-11, 15-20). B) Ordinal network layers showing unweighted edges between individuals within time windows. Like edge overlap, individuals were more connected in time windows 1, 6-11, and 15-20, compared to 2-5 and 12-15. C) Graph strength within time windows showing individuals as thin grey lines and mean across individuals as thick grey lines. Graph strength peaked in time window 9, with noticeable higher strength than the following year.

>>>>

# Results
Individuals in multilayer networks became more connected as the spatial distance
<!-- JWT: I really think calling it spatial distance is misleading given we want to represent social scale. Even if we stick with calling it spatial distance (I see you call it social distance in the graph), we need to lead in calling it social scale so the reader knows that's what we're referencing. -->
threshold increased. Mean graph strength differed across habitat layers with
similar and higher graph strength in open and forage layers, and lower strength
in forest layers (Figure \@ref(fig:socres)). Individual graph strength increased
sharply between 5 m and 100 m in all three habitat classes followed by a plateau in
the rate of increase after 100 m (<!--TODO: figure XX-->). 
These results suggest the optimal social scale at
which groups should be assigned is between ~20 - 100 m based on
the rate at which network metrics <!--QW: which metrics?--> stabilized. For ungulates, groups are often
assigned based on 50 m threshold (Lingle 2003; Lesmeries et al. 2018; Peignier
et al. 2019), suggesting that given similar quantities of data, ~50 m is likely
an appropriate social scale for generating social networks in caribou and
similar species. <!--QW: I'm not sure about this statement. Should it be more about 
how GPS data allows (e.g. from this study and Peignier et al; Lesmerises et al.) us to confirm 
the use of 50m buffer that has long been used for studies in the field (e.g. Lingle 2003 and 
any Clutton-Brock red deer paper that uses group size data)-->

Increasing land cover resolution resulted in decreased availability of foraging habitat 
<!--QW: I think we need to call this foraging habitat, when possible... forage to me 
refers to the thing an animal is eating-->,
a rare and patchy habitat, and corresponding low connectivity of individuals in
these habitats at higher resolution (Figure \@ref(fig:lcres)). Graph strength
and edge overlap were relatively consistent across land cover resolutions for
forest and open layers (Figure \@ref(fig:lcres) D, E). Edge overlap decreased
sharply between 30 m and 600 m in forage layers, afterwards remaining stable to
1000 m (Figure \@ref(fig:lcres) D). Graph strength was more variable within
foraging habitat layers across land cover resolutions than open and forest habitat layers (Figure
\@ref(fig:lcres) D). <!-- JWT: the order things are discussed here is a little confusing, you discuss strength, edge overlap, then strenght again. I think this should be reordered so it's easier to follow. -->
The proportion of relocations in forest and open habitats
increased with increasing spatial resolution, while decreasing in foraging habitat
(Supplementary 1 Figure 1).  Overall, these results indicate the importance of
matching land cover resolution to scale of selection as well as ensuring the
land cover product used has a resolution fine enough to detect landscape
features and habitats relevant to study species, such as important patchy and
rare habitats.
<!--QW: what makes it ordinal again? Is it ordinal OR continuous? -->
The ordinal multilayer network generated indicated within-year time windows of
increased caribou sociality. <!--QW: I'm not sure what you are trying to say in this first sentence. Is it that there are distinct within-year time windows where social network metrics increased? -->
Edge overlap was higher in time windows 1, 6-11 and
15-20 than in time windows 2-5 and 12-15  (Figure \@ref(fig:temp) A). <!--QW: I'm not sure about using the window number - it doesn't really mean anyhting. Can you use actual dates?--> Time
windows of higher edge overlap, between approximately October and May, had
correspondingly higher graph strength compared to time windows of lower edge
overlap, between approximately May and October (Figure \@ref(fig:temp) C). Graph
strength peaked across the time series in periods 9 and 10. These results
suggest that ordinal multilayer networks can effectively capture discrete time
windows of aggregation and dissaggregation related to resource availability, and
highlight the importance of carefully selecting the temporal scale of analysis.

@@

<!-- Figure: metrics by social scale -->
(ref:socres) Varying scale in social distance threshold. For each social distance threshold (100 - 1000 m by steps of 100 m), multilayer networks were constructed of caribou social associations (*R. tarandus*, n = `r DT[, uniqueN(get(idcol))]` females) on Fogo Island, Newfoundland between `r DT[, format(min(datetime), '%F')]` and `r DT[, format(max(datetime), '%F')]` across three habitat classes (forage, forest, and open). Graph strength (mean of individuals in bold) showed a sharp increase between 5 m and 100 m for all habitat classes. After 100 m, graph strength continued to increase at a slower rate. Open and forage layers showed higher variation in graph strength between individuals while the forest layer had less variation and lower mean graph strength.

<!-- Figure: metrics by land cover resolution -->
(ref:lcres) Varying spatial scale of land cover raster. For each land cover resolution (5, 25, 50, 75, 100, 250 and 500 m), multilayer networks were constructed of caribou social associations (*R. tarandus*, n = `r DT[, uniqueN(get(idcol))]` females) on Fogo Island, Newfoundland between `r DT[, format(min(datetime), '%F')]` and `r DT[, format(max(datetime), '%F')]` across three habitat classes (forage, forest, and open). A, B, C) Three land cover rasters: the original resolution (30 m) and two aggregated rasters (500 m and 1000 m). D) Edge overlap of habitat layers across spatial resolutions. Open and forest layers show consistent edge overlap with increasing spatial resolution while forage shows a sharp decline in edge overlap between 30 m and 600 m. Above 600 m, the forage layers are stable. E) Graph strength (mean of individuals in bold) within habitat layers across spatial resolution. Forage layers showed high variation in graph strength with many individuals dropping to 0 after 500 m and others increasing with spatial resolution. Open layers and forest layers were relatively stable across spatial resolutions, with higher mean graph strength in open compared to forest.

<!-- Figure: metrics by number of observations -->
(ref:nobs) Varying scale in number of observations. Multilayer networks were generated using a  sample number of observations (10 - 1000 observations by steps of 10) of caribou social associations (*R. tarandus*, n = `r DT[, uniqueN(get(idcol))]` females) on Fogo Island, Newfoundland between `r DT[, format(min(datetime), '%F')]` and `r DT[, format(max(datetime), '%F')]` across three habitat classes (forage, forest, and open). A) Graph strength was highly variable at low number of observations (less than 100) for all habitat layers and relatively stable after 200 observations. B) Edge overlap increased for all habitat layers with increasing number of observations. Open and forage layers had higher edge overlap than forest layers. C) Multidegree increased for all individuals with increasing number of observations. Individuals showed high variability (`r nobs[nobs == max(nobs), paste(range(multideg), collapse = ' - ')]`) at the maximal number of observations (1000).

<!-- Figure: Time window -->
(ref:temp) Varying temporal scale in multilayer networks. Multilayer networks were generated of caribou social associations (*R. tarandus*, n = `r DT[, uniqueN(get(idcol))]` females) on Fogo Island, Newfoundland within ordinal time windows (20 ordinal sample periods of 35-36 days) between `r DT[, format(min(datetime), '%F')]` and `r DT[, format(max(datetime), '%F')]`. A) Edge overlap across time windows showed two periods of low overlap (time windows 2-5 and 12-15), and three periods of high overlap (time windows 1, 6-11, 15-20). B) Ordinal network layers showing unweighted edges between individuals within time windows. Like edge overlap, individuals were more connected in time windows 1, 6-11, and 15-20, compared to 2-5 and 12-15. C) Graph strength within time windows showing individuals as thin grey lines and mean across individuals as thick grey lines. Graph strength peaked in time window 9, with noticeable higher strength than the following year.

<!-- JWT: edge overlap, graph strength, and multidegree are presented in different orders in the graphs. They should be presented in the same order each time even if the combination of what you show changes. -->
